Rheologic constraints on the upper mantle from five years of postseismic deformation following the El Mayor-Cucapah earthquake

### 2016-07-08 JGRAnnotatedRevision/new.tex
made a directory containing submission materials

\begin{figure}
\includegraphics[scale=0.9]{Figures/2016jb013114-f13}
\centering 
\caption{Mean chi-squared value for the best fitting slip model as a function of the transient shear modulus relative to the elastic shear modulus in a Zener upper mantle. Large dot indicates our preferred ratio.}
\label{fig:ShearModulusRatio}
\end{figure}

@@

The postseismic displacements predicted by our preferred Zener model are shown in Figures \ref{fig:NearField}, \ref{fig:FarField} and \ref{fig:RecordSectionMain}.  The largest misfit occur within the Imperial Valley and there does not appear to be any systematic trend in the residuals.  This suggests that the large errors are due to localized processes such as fault slip in the Imperial Valley triggered by the El Mayor-Cucapah earthquake \citep{Wei2011a,Wei2015}.  We do not see any pattern in the residuals that would suggest a laterally heterogeneous viscosity structure, which has been explored by \citet{Pollitz2012} and \citet{Rollins2015}.  We do notice regional scale seasonal oscillations in the lateral and vertical components of the residuals with an amplitude of 1-2 millimeters.  This is the result of our method for data processing which is not able to completely remove the seasonal signal in the GPS data, which was discussed in Section \ref{sec:Data}.  Additionally, we see systematic misfit in the later postseismic period west of the Landers and Hector Mine earthquakes, which may be the result of unmodeled postseismic deformation following those earthquakes.  Lastly, there are clear discrepancies between the observed and predicted vertical displacements following the first year after the El Mayor-Cucapah earthquake. We observe a broad uplift throughout Southern California which is inconsistent with any postseismic model.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Or, to use BibTeX:
%
% Follow these steps
%
% 1. Type in \bibliography{<name of your .bib file>} 
%    Run LaTeX on your LaTeX file.
%
% 2. Run BiBTeX on your LaTeX file.
%
% 3. Open the new .bbl file containing the reference list and
%   copy all the contents into your LaTeX file here.
%
% 4. Run LaTeX on your new file which will produce the citations.
%
% AGU does not want a .bib or a .bbl file. Please copy in the contents of your .bbl file here.

@@

\bibitem[{\textit{Freed et~al.}(2006)\textit{Freed, B{\"{u}}rgmann, Calais, Freymueller, and Hreinsd{\'{o}}ttir}}]{Freed2006a}
Freed, A.~M., R.~B{\"{u}}rgmann, E.~Calais, J.~Freymueller, and S.~Hreinsd{\'{o}}ttir (2006), {Implications of deformation following the 2002 Denali, Alaska, earthquake for postseismic relaxation processes and lithospheric rheology}, \textit{Journal of Geophysical Research: Solid Earth}, \textit{111}{B01401}, 1--23, \doi{10.1029/2005JB003894}.

>>>>

\begin{figure}
\includegraphics[scale=0.9]{Figures/2016jb013114-f13}
\centering 
\caption{Mean chi-squared value as a function of the transient shear modulus relative to the elastic shear modulus in a Zener rheology upper mantle. Large dot indicates our preferred ratio.}
\label{fig:ShearModulusRatio}
\end{figure}

@@

The postseismic displacements predicted by our preferred Zener model are shown in Figures \ref{fig:NearField}, \ref{fig:FarField} and \ref{fig:RecordSectionMain}.  The largest misfit occur within the Imperial Valley where there does not appear to be any systematic trend in the residuals.  This suggests that the large errors are due to localized processes such as fault slip in the Imperial Valley triggered by the El Mayor-Cucapah earthquake \citep{Wei2011a,Wei2015}.  We do not see any pattern in the residuals that would suggest a laterally heterogeneous viscosity structure, which has been explored by \citet{Pollitz2012} and \citet{Rollins2015}.  We do notice regional scale seasonal oscillations in the lateral and vertical components of the residuals with an amplitude of 1-2 millimeters.  This is the result of our method for data processing which is not able to completely remove the seasonal signal in the GPS data, which was discussed in Section \ref{sec:Data}.  Additionally, we see systematic misfit in the later postseismic period west of the Landers and Hector Mine earthquakes, which may be the result of unmodeled postseismic deformation following those earthquakes.  Lastly, there are clear discrepancies between the observed and predicted vertical displacements following the first year after the El Mayor-Cucapah earthquake. We observe a broad uplift throughout Southern California which is inconsistent with any postseismic model.

@@

@@

\bibitem[{\textit{Freed et~al.}(2006)\textit{Freed, B{\"{u}}rgmann, Calais, Freymueller, and Hreinsd{\'{o}}ttir}}]{Freed2006a}
Freed, A.~M., R.~B{\"{u}}rgmann, E.~Calais, J.~Freymueller, and S.~Hreinsd{\'{o}}ttir (2006), {Implications of deformation following the 2002 Denali, Alaska, earthquake for postseismic relaxation processes and lithospheric rheology}, \textit{Journal of Geophysical Research: Solid Earth}, \textit{111}(B01401), 1--23, \doi{10.1029/2005JB003894}.
